% Using LuaLaTeX for this, compile twice for proper page numbers.
% Just using an article class - means extra parameters in the header area.
\documentclass[11pt]{article}
\usepackage{polyglossia}
\setdefaultlanguage{english}
\usepackage[utf8x]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage[expansion=true,protrusion=true]{microtype}
\usepackage[top=1.25in,bottom=1.25in,left=1.3in,right=1.5in]{geometry}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text,Numbers=OldStyle,Contextuals=Alternate,Ligatures=Contextual,ItalicFeatures={Ligatures=Contextual}]{Linux Libertine}[SmallCapsFeatures=
	{LetterSpace=7.5},WordSpace={1.5,1.5,1.5}]
\setsansfont[Mapping=tex-text]{Linux Biolinum}[SmallCapsFeatures=
	{LetterSpace=7.5},WordSpace={1.75,1.75,1.75}]
\newfontfamily\headerfont[LetterSpace=12,WordSpace={2,2,2}]{Raleway ExtraBold}
\usepackage{lastpage}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\usepackage{titlesec}
\titlespacing\section{0pt}{0pt plus 2pt minus 2pt}{8pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}
{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titleformat{\section}
{\vspace{15pt}{\titlerule[1.4pt]}\vspace{0.1em}}
{\thesection}{-2.8em}{\headerfont\bfseries\footnotesize\MakeUppercase}
\titleformat{\subsection}
{\vspace{-0.5ex}}{\thesubsection}{0em}{\large\scshape}
\titleformat{\subsubsection}
{}{\thesubsection}{-3em}{\footnotesize\bfseries\textsf}
\usepackage{enumitem}
\setlist{nolistsep}
\setlist[itemize]{leftmargin=0.5cm, rightmargin=0.5cm}
\usepackage{multicol}
\frenchspacing
\pagestyle{fancy}

% I like my name and page number on the footer.
\cfoot{}
\rfoot{\textsf{\scshape{Your Name Here} | \thepage\ of \pageref{LastPage}}}
% =============================================================================

\newcommand{\MyName}[1]{
		\Huge \begin{center} \textsf{\textsc{#1}} \end{center}
		\vspace{-20pt} \par \normalsize \normalfont
		}

\newcommand{\MyInformation}[1]{
		\large \begin{center} \textsf{\scshape{#1}} \end{center}
		\vspace{-15pt} \par \normalsize \normalfont
		}

% =============================================================================
% =============================================================================

\begin{document}
\thispagestyle{empty}
\MyName{Your Name}
\MyInformation{1000 S. 5\textsuperscript{th} St. Apt 100, City, ST, 75309 \\
               800 867 5390 --- \Large \href{mailto:your_email@email.com}
	          {your\_email@email.com}
}

% =============================================================================

\section*{Education}
\subsection*{Great University \hfill 2015--2020 (Est.)}
Ph.D. in Basket Weaving

Advisor: Dr. Scientist Man

\subsection*{University of Meh \hfill 2008--13}
B.S. in Toe Cutting

\subsection*{State College \hfill 2006--08}

% =============================================================================

\section*{Employment}
\subsection*{Company Name \hfill 2015--Present}

\begin{itemize}
\subsubsection*{Position Title \hfill 2016--Present}
\item Analyzed Stuff
\item Trained People
\item Wrote Things
\item Taught People

\subsubsection*{Other Position \hfill Spring 2018}
\item Instructed People

\subsubsection*{Even More Positions \hfill Fall 2015}
\item Educated People
\end{itemize}

\subsection*{Different Company \hfill 2008--15}
\begin{itemize}
\subsubsection*{Position \hfill 2014--15}
\item Determined things
\item Traveled to places

\subsubsection*{Different Position \hfill 2013--14}
\item Managed people

\subsubsection*{Third Position \hfill 2009--10}
\item Coordinated events
\item Communicated things to people

\subsubsection*{Fourth position \hfill 2008--13}
\item Built things
\end{itemize}

% =============================================================================

\section*{Research Experience}
\subsection*{Great University \hfill 2015--Present}
\begin{itemize}
\subsubsection*{Researcher in Dr. Awesome Man's Research Group
\hfill 2015--Present}
\item Developed science
\item Authored software
\item Combined techniques
\subsubsection*{Mentor \hfill 2016--Present}
Mentored undergraduate students 
\end{itemize}

% =============================================================================

\section*{PUBLICATIONS}

\subsection*{In Preparation}

\begin{itemize}[label={},itemsep=7pt]

\item \textbf{Your Name}; Co-author; End Author.
``Title of Publication''
\textit{Submitted for Review to Journal Name}

\end{itemize}

\subsection*{Peer-Reviewed}

\begin{itemize}[label={},itemsep=7pt]

\item \textbf{Your Name}; Co-author; Corresponding author.
``Other Publication Title''
\textit{Journal Name}
\textbf{2018},
\textit{32} (10),
Pages--Pages

\item \textbf{Your Name}; Co-author; Corresponding author.
``Other Publication Title''
\textit{Journal Name}
\textbf{2018},
\textit{32} (10),
Pages--Pages
\end{itemize}

% =============================================================================

\section*{Presentations}
\begin{itemize}[label={},itemsep=7pt]

\item \textbf{Your Name}; Other People; Final Author.
``Title of Presentation''
\textit{Conference Name},
City, ST,
June 4\textsuperscript{th}, \textbf{2019}
(Poster)

\item \textbf{Your Name}; Other People; Final Author.
``Title of Presentation''
\textit{Conference Name},
City, ST,
June 4\textsuperscript{th}, \textbf{2019}
(Oral)

\end{itemize}

% =============================================================================

\section*{Awards and Scholarships}
\subsubsection*{Outstanding Award \hfill April 2019}
\subsubsection*{Kickass win (1\textsuperscript{st} place) \hfill April 2018}
\subsubsection*{Boring Scholarship \hfill Spring 2008}

% =============================================================================

\section*{Professional Service}
\subsubsection*{Service \hfill 2016--19}
\subsubsection*{Service \hfill 2017, 2019}


% =============================================================================

\section*{Skills and Personality}
\begin{itemize}
	\item Willing to travel
	\item Enjoys presentations and public speaking
	\item Award winning smile
	\item Able to learn new skills quickly
\end{itemize}
\end{document}
